\begin{abstract}
    Edge Cloud Computing enables computational tasks, such as machine learning models or other AI algoriuthms,
    to be processed at the edge of the network using limited
    computational resources in comparison to larger remote data centres. Because of this, resource allocation and
    management is significantly more important. Existing resource allocation approaches usually assume that tasks
    have inelastic resource requirements (i.e., a fixed amount of bandwidth and computation requirements). However,
    this may result in inefficient resource usage due to unbalanced requirements from tasks that can cause
    bottlenecks. To address this, we propose a novel approach that takes advantage of the elastic nature of resources
    as to time taken for an operation to occur is generally proportional to the allocated resource. This, however,
    makes previous research incompatible with such elasticity. Therefore, we describe this problem formally as an
    optimisation problem and propose a scalable approximation algorithm. To deal with self-interested users, we use a
    technique from multi-agent systems and design to demonstrate a centralised auction mechanism that is incentive
    compatible using the approximation algorithm.
    Moreover, we propose a novel Decentralised Iterative Auction that does not require users to reveal their private
    task value. Using extensive simulations, we show that considering the elasticity of resources leads to a gain in
    utility of around 20\% compared to existing approaches, with the proposed approaches typically achieving 95\% of
    the theoretical optimal.
\end{abstract}