%! Suppress = MissingImport
%%
%% sample document for AAMAS'19 conference
%%
%% modified from sample-sigconf.tex
%%
%% see ACM instructions acmguide.pdf
%%
%% AAMAS-specific questions? F.A.Oliehoek@tudelft.nl
%%

\pdfminorversion=7  % Fixes .eps image files

\documentclass[sigconf]{aamas}  % do not change this line!
%% your usepackages here, for example:
\usepackage{booktabs}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{appendix}
\usepackage{soul}
\usepackage{balance}
\usepackage[]{todonotes}

%% do not change the following lines
\setcopyright{ifaamas}  % do not change this line!
\acmDOI{doi}  % do noadat change this line!
\acmISBN{}  % do not change this line!
\acmConference[AAMAS'20]{Proc.\@ of the 19th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2020), B.~An, N.~Yorke-Smith, A.~El~Fallah~Seghrouchni, G.~Sukthankar (eds.)}{May 2020}{Auckland, New Zealand}  % do not change this line!
\acmYear{2020}  % do not change this line!
\copyrightyear{2020}  % do not change this line!
\acmPrice{}  % do not change this line!


%% the rest of your preamble here
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
  basicstyle=\small,
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Auction-based Mechanisms for Allocating Elastic Resources in Edge Clouds}
%\titlenote{Produces the permission block, and copyright information}

% AAMAS: as appropriate, uncomment one subtitle line; check the CFP
%\subtitle{Extended Abstract}
%\subtitle{Industrial Applications Track}
%\subtitle{Socially Interactive Agents Track}
%\subtitle{Blue Sky Ideas Track}
%\subtitle{Engineering Multiagent Systems Track}
%\subtitle{Robotics Track}
%\subtitle{JAAMAS Track}
%\subtitle{Doctoral Mentoring Program}

%\subtitlenote{The full version of the author's guide is available as \texttt{acmart.pdf} document}


% AAMAS: submissions are anonymous for most tracks
\author{Paper \#1263}  % put your paper number here!

%% example of author block for camera ready version of accepted papers: don't use for anonymous submissions
%

\begin{abstract}  % put your abstract here!
Edge cloud computing enables computational task to be process at the edge of the network using limited computational
resource in comparison to larger remote data centres. Because of this, resource allocation and management is
significantly more important. Existing resource allocations approaches usually assumed that tasks have inelastic
resource requirements (i.e., a fixed amount of bandwidth and computation requirements) however this may result in
inefficient resource usage due to unbalanced requirements from tasks resulting in resource bottlenecks. To address
this, we propose a novel approach that takes advantage of the elastic nature of resource as time taken for an operation
to occur is proportional to the resource allocated. This however make previous research incompatible with this problem.
Therefore we describe this problem formally, show that it is NP-Hard and propose a scalable approximation algorithm.
To deal with self-interested user, we demonstrate a centralised auction mechanism that is incentive compatible using
the approximation algorithm. Moreover, we propose a novel decentralised iterative auction mechanism that doesn't
require users to reveal their private task value but is not incentive compatible. In extensive simulations, we show
that considering the elasticity of resources leads to a gain in utility of around 20\% compared to existing approaches
with the proposed approaches typically achieving 95\% of the theoretical optimal.
\end{abstract}


% AAMAS: the ACM CCS are not needed within AAMAS papers
%%
%% The code below should be generated by the tool at
%% http://dl.acm.org/ccs.cfm
%% Please copy and paste the code instead of the example below.
%%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010575.10010755</concept_id>
%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Networks~Network reliability</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}


\keywords{Edge clouds; elastic resources; auctions}  % put your semicolon-separated keywords here!

\maketitle

%% start of main body of paper

\include{paper}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% bibliography: see CFP for number of permitted pages
\balance
\bibliographystyle{ACM-Reference-Format}  % do not change this line!
\bibliography{bibliography}  % put name of your .bib file here

\end{document}